Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-08-23 figures_Paper1/energy_setup_old.tex
Final version paper 23.08.2022

\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\usetikzlibrary{math}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{matrix}
\usetikzlibrary{intersections}
\usetikzlibrary{bending}
\usepgfplotslibrary{fillbetween}

@@

% compilation of figure raises warning: Dimension too large, since the axis environment
% is clipped. This is warning can be ignored.
\clip (-3.5,-12.3) -- (5.5,-12.3) -- (5.5,5.3) -- (-3.5,5.3) -- cycle;

% Figure 1
\begin{scope}
% r-lead
% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;
\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
\draw[draw=hgreen] (0,2) -- (0,3);
% UHB
\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
\draw[draw=hgreen] (0,3) -- (0,5);
% \draw (0,4) -- (5,4);
% LHB
\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
\draw[draw=hgreen] (0,0) -- (0,2);
% \draw (-3,1) -- (3,1);
% l-lead
% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% r-lead width
\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (4.7,2.5) edge node[midway,right] {$W_{\text{b}}$} (4.7,5.5);
% % chemical potential right
% \draw[line width=1pt] (2.5,2.75) -- node[midway,below] {$\mu_{\text{r}}$} (4.5,2.75);
%gap
% \path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge node[midway,right] {$\Delta_{\text{eff}}$/$\Delta_{\text{eff},\text{ph}}$} (0,3.5);
\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0.5,1.5) edge node[midway,right] {$\Delta_{\text{pg}}$} (0.5,3.5);
% % chemical potential left
% \draw[line width=1pt] (-2.5,2.25) -- node[midway,above] {$\mu_{\text{l}}$} (-0.5,2.25);
% l-lead width
\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (-2.7,-0.5) edge node[midway,left] {$W_{\text{b}}$} (-2.7,2.5);

% text
\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UHB}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};

\node at (-2.5,4.5) {\bfseries(a)};
\end{scope}

% r-lead
% (position of lead has to be set manually)
\begin{axis}[%
xmin=0,xmax=3.5,
ymin=-5,ymax=5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
at={(2.5cm,1.15cm)}]

\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);

\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];

\draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
\end{axis}

% l-lead
% (position of lead has to be set manually)
\begin{axis}[%
ymin=-5,ymax=5,
xmin=0,xmax=3.5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
clip mode=individual,
at={(-2.5cm,-1.85cm)}]

\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);

\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];

\draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
\end{axis}

% Figure 2
\begin{scope}[yshift=-6cm]
% % r-lead
% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
\draw[draw=hgreen] (0,2) -- (0,3);
% UHB
\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
\draw[draw=hgreen] (0,3) -- (0,5);
% LHB
\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
\draw[draw=hgreen] (0,0) -- (0,2);
% % l-lead
% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text
\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UHB}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};

\node at (-2.5,4.5) {\bfseries(b)};

@@

% particles
\draw[dotted,color=black,fill=white] (0.5,1) circle[radius=3pt];
\draw[color=black,fill=hgreen] (0.5,3.9) circle[radius=3pt];
% driving
\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=140,in=-140,line width=1pt] (0.5,1) edge (0.5,3.9);
\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.0,3.5) -- (-0.3,2.5);
\node at (-1,3.5) {\textcolor{hyellow}{$\Omega$}};
% escape
\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.5,3.9) edge (3.2,3.9);

@@

% r-lead
% (position of lead has to be set manually)
\begin{axis}[%
xmin=0,xmax=3.5,
ymin=-5,ymax=5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
at={(2.5cm,-4.85cm)}]

\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);

\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];

% \draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
\end{axis}

% l-lead
% (position of lead has to be set manually)
\begin{axis}[%
ymin=-5,ymax=5,
xmin=0,xmax=3.5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
clip mode=individual,
at={(-2.5cm,-7.85cm)}]

\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);

\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];

% \draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
\end{axis}

% Figure 3
\begin{scope}[yshift=-12cm]
% % r-lead
% \filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
\fill[fill=hgreen!20!white] (0,3) -- (0,2) -- (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm] -- cycle;
\draw[draw=hgreen] (0.2,1.99) arc [start angle=195, end angle=165,x radius=2cm, y radius=2cm];
\draw[draw=hgreen] (0,2) -- (0,3);
% UHB
\fill[fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,5) arc [start angle=90, end angle=-84.7,x radius=2cm, y radius=1cm]; 
\draw[draw=hgreen] (0,3) -- (0,5);
% LHB
\fill[fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
\draw[draw=hgreen] (0,0) arc [start angle=-90, end angle=84.5,x radius=2cm, y radius=1cm];
\draw[draw=hgreen] (0,0) -- (0,2);
% % l-lead
% \filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text
\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
\node at (1,4) [minimum size = 0.1 cm,xshift=0.2cm]{\textcolor{hgreen}{UHB}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
\node at (-1.8,1) [minimum size = 0.1 cm]{\textcolor{hred!20!white}{l-lead}};

\node at (-2.5,4.5) {\bfseries(c)};

@@

% particles
\draw[dotted,color=black,fill=white] (0.4,0.7) circle[radius=3pt];
\draw[dotted,color=black,fill=white] (0.4,4.8) circle[radius=3pt];
\draw[color=black,fill=hgreen] (0.4,3.25) circle[radius=3pt];
\draw[dotted,color=black,fill=white] (0.9,1.7) circle[radius=3pt];
\draw[color=black,fill=hgreen] (0.9,3.25) circle[radius=3pt];
% driving
\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.4,0.7) edge (0.4,4.8);
\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.0,3.5) -- (-0.3,2.5);
\node at (-1,3.5) {\textcolor{hyellow}{$\Omega$}};
% impact ionization
\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-60,in=60,line width=1pt] (0.4,4.8) edge (0.4,3.25);
\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.9,1.7) edge (0.9,3.25);
% escape
\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=30,in=150,line width=1pt] (0.4,3.25) edge (2.85,3.25);
\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten  <=0.15cm,out=-30,in=-150,line width=1pt] (0.9,3.25) edge (3.1,3.25);

@@

% r-lead
% (position of lead has to be set manually)
\begin{axis}[%
xmin=0,xmax=3.5,
ymin=-5,ymax=5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
at={(2.5cm,-10.85cm)}]

\addplot[solid,domain=-5:2,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-5:2,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x+2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-5) -- (axis cs:0,2);

\addplot[fill=hred!20!white,domain=-5:2] fill between [of=spectrum and yaxis,soft clip={domain=-5:5}];
\addplot[fill=hred!60!white,domain=-5:2] fill between [of=occupation and yaxis,soft clip={domain=-5:5}];

% \draw[line width=1pt] (axis cs:0,-2.2) -- node[midway,below] {$\mu_{\text{r}}$} (1,-2.2);
\end{axis}

% l-lead
% (position of lead has to be set manually)
\begin{axis}[%
ymin=-5,ymax=5,
xmin=0,xmax=3.5,
xtick=\empty,
ytick=\empty,
axis line style={draw=none},
scale=1,
clip mode=individual,
at={(-2.5cm,-13.85cm)}]

\addplot[solid,domain=-2:5,hred,name path=spectrum,samples=200] ({1.*1.0^2/(x^2+1.0^2)},{x});
\addplot[solid,domain=-2:5,hred,name path=occupation,samples=200] ({1.*1.0^2/(x^2+1.0^2)*1./(exp((x-2.2)/0.06)+1.)},{x});
\path[name path=yaxis] (axis cs:0,-2) -- (axis cs:0,5);

\addplot[fill=hred!20!white] fill between [of=spectrum and yaxis,soft clip={domain=-2:5}];
\addplot[fill=hred!60!white] fill between [of=occupation and yaxis,soft clip={domain=-2:5}];

% \draw[line width=1pt] (axis cs:0,2.2) -- node[midway,above] {$\mu_{\text{l}}$} (1,2.2);
\end{axis}

>>>>

\usepackage{pgfplots}
\pgfplotsset{compat=1.13}
\usetikzlibrary{math}
\usetikzlibrary{calc}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{positioning}
\usetikzlibrary{fit}
\usetikzlibrary{matrix}
\usetikzlibrary{intersections}
\usetikzlibrary{bending}
\usepgfplotslibrary{fillbetween}

@@

% Figure 1
\begin{scope}
% r-lead
\filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
% UHB
\filldraw[draw=hgreen,fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
% LHB
\filldraw[draw=hgreen,fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
% l-lead
\filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% r-lead width
\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (4.7,2.5) edge node[midway,right] {$W_{\text{b}}$} (4.7,5.5);
% chemical potential right
\draw[line width=1pt] (2.5,2.75) -- node[midway,below] {$\mu_{\text{r}}$} (4.5,2.75);
%gap
% \path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge node[midway,right] {$\Delta_{\text{eff}}$/$\Delta_{\text{eff},\text{ph}}$} (0,3.5);
\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (0,1.5) edge node[midway,right] {$\Delta_{\text{pg}}$} (0,3.5);
% chemical potential left
\draw[line width=1pt] (-2.5,2.25) -- node[midway,above] {$\mu_{\text{l}}$} (-0.5,2.25);
% l-lead width
\path[>=stealth,<->,shorten >=0.5cm,shorten <=0.5cm,line width=2pt] (-2.7,-0.5) edge node[midway,left] {$W_{\text{b}}$} (-2.7,2.5);

% text
\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UHB}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
\node at (-1.5,1) [minimum size = 0.1 cm]{\textcolor{hred}{l-lead}};

\node at (-2.7,5) {\bfseries(a)};
\end{scope}

% Figure 2
\begin{scope}[yshift=-6cm]
% r-lead
\filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
% UHB
\filldraw[draw=hgreen,fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
% LHB
\filldraw[draw=hgreen,fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
% l-lead
\filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text
\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
\node at (1,4) [minimum size = 0.1 cm]{\textcolor{hgreen}{UHB}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
\node at (-1.5,1) [minimum size = 0.1 cm]{\textcolor{hred}{l-lead}};

\node at (-2.7,5) {\bfseries(b)};

@@

% particles
\draw[dotted,color=black,fill=white] (0.5,1) circle[radius=3pt];
\draw[color=black,fill=hgreen] (0.5,3.9) circle[radius=3pt];
% driving
\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.5,1) edge (0.5,3.9);
\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,3.5) -- (0,2.5);
\node at (-1,3.3) {\textcolor{hyellow}{$\Omega$}};
% escape
\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-30,in=-150,line width=1pt] (0.5,3.9) edge (3.2,3.9);

@@

% Figure 3
\begin{scope}[yshift=-12cm]
% r-lead
\filldraw[draw=hred,fill=hred!20!white] (2.5,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  
% UHB
\filldraw[draw=hgreen,fill=hgreen!20!white] (0,3) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
% LHB
\filldraw[draw=hgreen,fill=hgreen!20!white] (0,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;  % Hubbard bands as parabolas
% l-lead
\filldraw[draw=hred,fill=hred!20!white] (-2.5,0) arc [start angle=-90, end angle=90,x radius=2cm, y radius=1cm] -- cycle;

% text
\node at (3.5,4) [minimum size = 0.1 cm]{\textcolor{hred}{r-lead}}; 
\node at (1,4) [minimum size = 0.1 cm,xshift=0.2cm]{\textcolor{hgreen}{UHB}};
\node at (1,1) [minimum size = 0.1 cm]{\textcolor{hgreen}{LHB}};
\node at (-1.5,1) [minimum size = 0.1 cm]{\textcolor{hred}{l-lead}};

\node at (-2.7,5) {\bfseries(c)};

@@

% particles
\draw[dotted,color=black,fill=white] (0.4,0.7) circle[radius=3pt];
\draw[dotted,color=black,fill=white] (0.4,4.8) circle[radius=3pt];
\draw[color=black,fill=hgreen] (0.4,3.25) circle[radius=3pt];
\draw[dotted,color=black,fill=white] (0.9,1.7) circle[radius=3pt];
\draw[color=black,fill=hgreen] (0.9,3.25) circle[radius=3pt];
% driving
\path[color=hyellow,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.4,0.7) edge (0.4,4.8);
\draw [->,>=Stealth,line width=1pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] (-2.5,3.5) -- (-0.3,2.5);
\node at (-1,3.3) {\textcolor{hyellow}{$\Omega$}};
% impact ionization
\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=-60,in=60,line width=1pt] (0.4,4.8) edge (0.4,3.25);
\path[>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=120,in=-120,line width=1pt] (0.9,1.7) edge (0.9,3.25);
% escape
\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten <=0.15cm,out=30,in=150,line width=1pt] (0.4,3.25) edge (2.9,3.25);
\path[color=hred,>=stealth,->,shorten >=0.15cm,shorten  <=0.15cm,out=-30,in=-150,line width=1pt] (0.9,3.25) edge (3.4,3.25);

@@

### 2022-08-23 figures_Paper1/setup_association.tex
Final version paper 23.08.2022

\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=horange] (axis cs:0,#1,0) -- (axis cs:1,#1,0);
   \draw[color=horange] (axis cs:0,#1,1) -- (axis cs:1,#1,1);
   \draw[color=horange] (axis cs:0,#1,2) -- (axis cs:1,#1,2);
   \draw[color=horange] (axis cs:0,#1,3) -- (axis cs:1,#1,3);
};

@@

\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=horange] (axis cs:3,#1,0) -- (axis cs:4,#1,0);
   \draw[color=horange] (axis cs:3,#1,1) -- (axis cs:4,#1,1);
   \draw[color=horange] (axis cs:3,#1,2) -- (axis cs:4,#1,2);
   \draw[color=horange] (axis cs:3,#1,3) -- (axis cs:4,#1,3);
};

@@

% coordinates for light

\coordinate (top1) at (axis cs:2,0.5,3);
\coordinate (top2) at (axis cs:2,1.5,3);
\coordinate (top3) at (axis cs:2,2.5,3);

% arrows for hoppings

\node at (axis cs:-0.1,3.5,-0.15) {\textcolor{hblue}{$\mu_{\text{r}}$}};
\node at (axis cs:5,3.5,-0.15) {\textcolor{hblue}{$\mu_{\text{l}}$}};
\node at (axis cs:2,2.8,-0.35) {\textcolor{hgreen}{$U,g$}};
\node at (axis cs:3.5,3,-0.25) {\textcolor{horange}{$\Gamma$}};
\node at (axis cs:1.3,3,-0.25) {\textcolor{black}{$v$}};

@@

% cw-light

\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top1)+(120:2) $) -- (top1);
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top2)+(115:2) $) -- (top2);
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top3)+(110:2) $) -- (top3);
% \draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.8cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top4)+(105:3) $) -- (top4);

>>>>

\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:0,#1,0) -- (axis cs:1,#1,0);
   \draw[color=hblue] (axis cs:0,#1,1) -- (axis cs:1,#1,1);
   \draw[color=hblue] (axis cs:0,#1,2) -- (axis cs:1,#1,2);
   \draw[color=hblue] (axis cs:0,#1,3) -- (axis cs:1,#1,3);
};

@@

\pgfplotsinvokeforeach{0,1,...,3} {
   \draw[color=hblue] (axis cs:3,#1,0) -- (axis cs:4,#1,0);
   \draw[color=hblue] (axis cs:3,#1,1) -- (axis cs:4,#1,1);
   \draw[color=hblue] (axis cs:3,#1,2) -- (axis cs:4,#1,2);
   \draw[color=hblue] (axis cs:3,#1,3) -- (axis cs:4,#1,3);
};

@@

% coordinates for light
\coordinate (top1) at (axis cs:2,0.5,3);
\coordinate (top2) at (axis cs:2,1.5,3);
\coordinate (top3) at (axis cs:2,2.5,3);

% arrows for hoppings 
\node at (axis cs:-0.1,3.5,-0.15) {\textcolor{hblue}{$\mu_{\text{r}}$}};
\node at (axis cs:5,3.5,-0.15) {\textcolor{hblue}{$\mu_{\text{l}}$}};
\node at (axis cs:2,2.8,-0.35) {\textcolor{hgreen}{$U,g$}};
\node at (axis cs:3,3,-0.25) {\textcolor{hred}{$\Gamma$}};
\node at (axis cs:1.3,3,-0.25) {\textcolor{black}{$v$}};

@@

% cw-light
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top1)+(120:2) $) -- (top1);
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top2)+(115:2) $) -- (top2);
\draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.4cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top3)+(110:2) $) -- (top3);
% \draw [->,>=Stealth,line width=2pt,decorate,decoration={snake,amplitude=0.2cm,segment length=0.8cm,pre length=0.4cm,post length=0.4cm},draw=hyellow] ($ (top4)+(105:3) $) -- (top4);
